---
title: "PA1_template"
author: "debocorne"
date: "9 de septiembre de 2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

* Code for reading in the dataset and/or processing the data

```{r }
if (!file.exists("data/repdata_data_activity")) {
        # download the data
        fileURL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
        zipfile="data/repdata_data_activity.zip"
        message("Downloading data")
        download.file(fileURL, destfile=zipfile, method="curl")
        unzip(zipfile, exdir="data/repdata_data_activity")
}

# Read in the data 

test.data <- read.csv( 'data/repdata_data_activity/activity.csv', header = TRUE, sep = ",")
```

 * Histogram of the total number of steps taken each day
 
```{r }
aggTotals <- aggregate(steps ~ date,test.data, sum,na.rm=TRUE)
hist(aggTotals$steps, xlab = "", col="Red", main = "Activity", font=3)

```

* Mean and median number of steps taken each day

```{r }
mean(aggTotals$steps)
median(aggTotals$steps)
```

* Time series plot of the average number of steps taken

```{r }

aggInterval <- aggregate(steps ~ interval,test.data, mean,na.rm=TRUE)
plot(aggInterval$steps, xlab = "", col="Red", main = "Activity steps by interval", font=3)
```

* The 5-minute interval that, on average, contains the maximum number of steps

```{r }
stepsInterval <- aggregate(steps ~ interval, test.data, mean)
plot(stepsInterval$interval, stepsInterval$steps, type="l", xlab = "5 min - interval", ylab = "Average steps", main = "Average Daily Activity Pattern", col = "green")
```

* Code to describe and show a strategy for imputing missing data

```{r }
navalue<-test.data
navalue[is.na(navalue$steps),"steps"]<-0
```

* Histogram of the total number of steps taken each day after missing values are imputed

```{r }
aggStepsDate <- aggregate(steps ~ date,navalue, sum)
hist(aggStepsDate$steps, xlab = "", col="Red", main = "Steps per day non NAs", font=3,breaks = 8)

```

* Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r }

aggStepsDate <- aggregate(steps ~ date,navalue, sum)

#png(file = "3.png", width = 480, height = 480)
hist(aggStepsDate$steps, xlab = "", col="Red", main = "Steps per day non NAs", font=3,breaks = 8)

mean(aggStepsDate$steps)

```
